Algorithmic and Economic Aspects of the Internet

### 2012-12-03 report/paper.tex
All the paper
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

\subsection{Totally open market}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\end{document}

>>>>

\subsubsection{Totally open market}

@@

The results of this experiment are fairly clear with 164 trials containing
non-zero trading and ZIC winning 115 of these with a median profit of 26973.0
versus a median profit of 0 for our agent the Wilcoxon test shows a clear
statisitical edge for ZIC (p < 0.01).

\subsubsection{Massive financial crash}

In this test we start with a fairly stable market with the price ranging
between 600 and 700. We then intentionally very rapidly crash the market by
dropping the price range to 1-100 for a short range of time before slowly
ramping the price back up.  Refer to figure 4 for the ask and bid orders
issued in one of the 300 example runs.

The rationale behind this is the fact that our agent tracks the equilibrium price
with some accuracy, and as such may be able to more efficiently issue a trade
than ZIC, which is placing its trades at random within the limit prices it has
been given.

In these conditions it is of course extremely difficult for any agent to act
within the market. We have also included a graph of our agent's equilibrium
estimator, this shows that the estimate does a pretty good job keeping up with
the extreme turbulence within the market.

In this experiment all 300 trials had cases where trading occurs. Of these 189
were lost by our agent, however, the medians had a significantly smaller
difference (ZIC 739.47, our agents 519.072136). Whilst this still represents a
statistically significant advantage (p < 0.01 Wilcoxon) for ZIC, it raises an
interesting case where the performance of our agent is significantly improved.
This lead us to our next experiment, which was to effectively repeatedly crash
and restore the market, causing an extremely high volatility.

\begin{figure}[h!] \includegraphics[width=80mm]{crash.png} \caption{Market
order prices given to both buyers and sellers. Extreme volatility introduced at
t=180 by suddenly crashing the market.} \end{figure}

\begin{figure}[h!]
\includegraphics[width=80mm]{crash2.png} \caption{Equilibrium estimate of both
our agent's buyer and seller versions} \end{figure}

\subsubsection{Square wave market}

In this experiment we start with the same inital conditions as the previous
market but we repeatedly change the price ranges from 600-700 and 1-100 and use
the "random" stepmode in an attempt to cause maximum market volatility.

The basic rationale of this experiment is that our agent performed better in
the volatile conditions of the previous experiment, but still performed worse
than ZIC. We wanted to see if this edge case might cause best case behaviour in
our agent. In figure 6 we have provided an example of what the orders placed look
like.

\begin{figure}[h!] \includegraphics[width=80mm]{squarewave.png} \caption{Market
order prices given to both buyers and sellers. Periodic volatility introduced
every 180 timesteps} \end{figure}

Unfortunately this experiment did not produce the expected results, with ZIC
managing to extract a much higher median profit than in the previous experiment
(1535.48). Our agent also extracted a slightly higher profit than the previous
experiment (median 703.82).

From these analysis we basically conclude that whilst our bot trades more
efficiently than giveaway it does not trade more efficiently than ZIC in both
stable and extremely unstable market conditions. Whilst this is disappointing
we find an obvious reason for this result: our implementation, which attempts
to follow the maths in the original Vytelingum\cite{Vytellingum:AA} paper,
there are flaws in the implementation which cause it not to trade anywhere near
as efficiently as expected, causing it to essentially fail to trade.

Our implementation also seems to issue significantly fewer trades than would be
expected
--luke expand this

\section{Analysing the other traders}

In this section we wanted to analyse the ZIP agent against all the others.
Based on the COMSM2006\cite{cliff:lecture} lecture about trading agents.
Specifically the lecture references an article written by D. Cliff which is
meant to show a case where ZIC traders will not converge to the equilibrium
price of the market\cite{cliff:minimalint}.

%
% The following two commands are all you need in the initial runs of your .tex
% file to produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv} \bibliography{paper}  % sigproc.bib is the name of
the Bibliography in this case
% You must have a proper ".bib" file and remember to run: latex bibtex latex
% latex to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional \balancecolumns
\appendix \end{document}
